Testing atlantisom: true biomass output from Atlantis

### 2019-04-30 TrueBioTest.Rmd
save survey census file

@@

surveyB_fromN <- sample_survey_biomass(survey_testNall, surv_cv, wtage)

>>>>

#save for later use, takes a long time to generate
saveRDS(surveyB_frombio, file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))

@@

surveyB_fromN <- sample_survey_biomass(survey_testNall, surv_cv, wtage)
#save for later use, takes a long time to generate
saveRDS(surveyB_fromN, file.path(d.name, paste0(scenario.name, "surveyBfromNcensus.rds")))
